Word learning at the semantics pragmatics interface

### 2020-04-03 paper/supplementary_material.Rmd
small chnages to supplement

plot_aoa <- ggplot(plot_aoa_ratings, aes(x = reorder(item, mean_aoa), y = mean_aoa)) +
  geom_point(size =2, pch = 4)+
  ylab("Mean rated age of acquisition")+
  xlab("Object")+
  ylim(0,15)+
  geom_image(aes(image=image, y = mean_aoa+2), asp = 4)+
  theme_light()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

cor_plot_me <- as_tibble(ranef_me$item, rownames = "item") %>%
  left_join(aoa_ratings)%>%
  ggplot(., aes(x = mean_aoa, y = Estimate.Intercept))+
  geom_abline(intercept = 1, slope = -1, lty = 2, alpha = 1, size = .5)+
  geom_point(pch = 4, size = 2)+
  geom_smooth(method = "lm", col = "black", se = F, lty = 2, size = .5)+
  xlab("Rated age of acquisition")+
  ylab("Mutual exclusivity effect (model intercept)")+
  ylim(-1,1)+
  stat_cor(method = "pearson", label.x = 7, label.y = .99)+
  theme_few()
```

@@

```{r fig2, include = T, fig.align = "center", fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1))
```

>>>>

plot_aoa <- ggplot(plot_aoa_ratings, aes(x = reorder(item, mean_aoa), y = mean_aoa)) +
  geom_point(size =2, pch = 4, aes(col = item))+
  ylab("Mean rated age of acquisition")+
  xlab("Object")+
  ylim(0,15)+
  geom_image(aes(image=image, y = mean_aoa+2), asp = 4)+
  theme_light()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_colour_viridis_d()+
  guides(col = F)

@@

cor_plot_me <- as_tibble(ranef_me$item, rownames = "item") %>%
  left_join(aoa_ratings)%>%
  ggplot(., aes(x = mean_aoa, y = Estimate.Intercept))+
  geom_point(pch = 4, size = 2, aes(col = item))+
  geom_smooth(method = "lm", col = "black", se = F, lty = 2, size = .5)+
  xlab("Rated age of acquisition")+
  ylab("Mutual exclusivity effect (model intercept)")+
  ylim(-1,1)+
  stat_cor(method = "pearson", label.x = 6, label.y = .99)+
  theme_few()+
  scale_colour_viridis_d()+
  guides(col = F)
```

@@

```{r fig2, include = T, fig.align = "center", fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
```
